### 2016-12-12 paper/chapters/vae.tex
added argument for regularizer for VAE
added figure for reparameterization trick

\paragraph{Regularization term $\mathcal{L}_{reg}$} encourages the model to learn simple representations in latent space, due to the negative Kullback-Leibler (KL) divergence between the learned variational distribution $q_\theta(z|x)$ and the latent space prior distribution $p(z)$.

@@

>>>>

\paragraph{Regularization term $\mathcal{L}_{reg}$} encourages the model to learn simple representations in latent space, due to the negative Kullback-Leibler (KL) divergence between the learned variational distribution $q_\theta(z|x)$ and the latent space prior distribution $p(z)$.
The regularizer also prevents the model from collapsing into a single point.

@@

\begin{figure}
  \centering
  \begin{tabular}{c:c}
    \subcaptionbox{without reparameterization}{\includestandalone[height=0.4\linewidth]{media/reparameterization_trick_without}}
      \quad \quad
    &
      \quad

    \subcaptionbox{with reparameterization applied}{\includestandalone[height=0.4\linewidth]{media/reparameterization_trick_with}}\\
  \end{tabular}
  \caption{reparameterization trick}
  \medskip
  \small
  Function $f_\theta(x)$ with inputs $x$ and (variational) parameters $\theta$ shown as directed graphical model.\\
  Left without and on the right with the reparameterization trick applied.\\
  Solid arrows show the forward pass and dashed arrows the error backpropagation.
  Rectangular nodes represent deterministic functions while circles indicate stochastic variables.
  Note that backpropagation of gradients through stochastic nodes is problematic and adds bias (verify!)
\end{figure}
